Appendix B

### 2021-11-07 Appendix-B.Rmd
* Knitting with appendix is now possible.
The font issue rooted from Siraji's OS.

```{r facIdFigAppB, eval=FALSE, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE, include=FALSE, out.height="100%", out.width="100%"}
cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")

>>>>

```{r facIdFigAppB, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE,  out.height="100%", out.width="100%"}
cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")

### 2021-11-07 Appendix-B.tex
* Knitting with appendix is now possible.
The font issue rooted from Siraji's OS.

\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}

@@

{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1}

@@

\caption{Correlation plot of the items}(\#fig:figCorAppB)
\end{figure}

@@

\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}

@@

{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/EFAResidualsAppB-1}

@@

\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB)
\end{figure}
\end{appendix}

>>>>

\caption{\label{tab:tabDesAppB-30}Descriptive Statistics for Unmerged response options}

@@

{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-32-1}

@@

\caption{Correlation plot of the items}(\#fig:figCorAppB-32)
\end{figure}

{\centering \includegraphics[width=1\linewidth,height=1\textheight]{manuscript_files/figure-latex/facIdFigAppB-36-1}

\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB-36)
\end{figure}

@@

\caption{\label{tab:EFATableAppB-39}Factor loadings and communality of the retained items [Unmerged Responses]}

@@

{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/EFAResidualsAppB-40-1}

@@

\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB-40)
\end{figure}
\end{appendix}

### 2021-11-07 manuscript.Rmd
* Knitting with appendix is now possible.
The font issue rooted from Siraji's OS.

#To find and install required dependencies.
packrat::restore()
#Only use when you have added some pack
packrat::snapshot(ignore.stale=TRUE)

@@

\blandscape

@@

\elandscape

@@

```{r clean, eval=FALSE, include=FALSE}
cleanFolder <- function() {
  answer <- NA
  while(!(answer %in% c('y', 'n'))) {
    answer <- readline(paste("Clean ", getwd(),"? (y/n)"))
  }
  if(answer == 'y') {
    rules <- c('.log', '.vrb', '.nav', '.snm', '.toc', 
               '-tikzDictionary', '.tex', '.synctex.gz')
    file.remove(list.files(pattern = paste0('\\',rules ,'$', collapse = '|')))
  }
}
cleanFolder()
```

@@

>>>>

#To find and install required dependencies.
packrat::restore()
#Only use when you have added some pack
#packrat::snapshot(ignore.stale=TRUE)

@@

@@

@@

```{r clean, eval=FALSE, include=FALSE}
cleanFolder <- function() {
  answer <- NA
  while(!(answer %in% c('y', 'n'))) {
    answer <- readline(paste("Clean ", getwd(),"? (y/n)"))
  }
  if(answer == 'y') {
    rules <- c('.log', '.vrb', '.nav', '.snm', '.toc', 
               '-tikzDictionary', '.tex', '.synctex.gz')
    file.remove(list.files(pattern = paste0('\\',rules ,'$', collapse = '|')))
  }
}
cleanFolder(y)
```

@@

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('instrument.Rmd')
```

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('Appendix-B.Rmd')
```

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('instrument.Rmd')
```

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('Appendix-B.Rmd')
```
